---
title: "`bookdown` examples"
author: "Ella Kaye"
date: "20/11/2017"
output: 
  bookdown::pdf_document2:
    toc: true
header-includes:
   - \usepackage{amsfonts}
bibliography: "test_bib.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Equations  {#sec:equations}

\begin{equation} 
  \mathbb{P}(X = k) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation}

See Equation \@ref(eq:binom).

# Theorems

```{theorem, pythag, name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse
and $a$ and $b$ denote the lengths of the other two sides, we have
$$a^2 + b^2 = c^2.$$
```

Theorem \@ref(thm:pythag) is very cool.

# Section and text references

In Section \@ref(sec:equations), I showed how to use equations.

(ref:cars) A scatterplot of the data `cars` using **base** R graphics.

```{r, cars, fig.cap = '(ref:cars)', echo = FALSE, fig.align='center'}
plot(cars)
```

Figure \@ref(fig:cars) is a boring plot.

# Citations
@testbook wrote interesting stuff. This is an exciting discovery [@testarticle].

# References